Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex

We report a favourable assessment of \tool over a diverse set of real-world
benchmarks.  Nevertheless, the set of benchmarks is limited within the scope
of this paper and \tool's performance may not generalise to other
application scenarios.  This can be addressed by expanding the benchmark set
in future experiments.

Furthermore, our algorithm for selecting the fixed-point precision to model
plant behaviour employs a heuristic based on user-provided controller
word-width specifications.  Given the encouraging results of our benchmarks,
this heuristic appears to be strong enough for the current benchmark set,
but this may not generalise.  Further experiments towards determining
suitable plant FWL configurations may thus be necessary in future work.

>>>>

We report a faviourable assessment of \tool over a diverse set of real-world
benchmarks. Nevertheless, this set of benchmarks is limited within the
scope of this paper and \tool's performance may not generalise to other
benchmark scenarios. This can be addressed by expanding the benchmark set
in future experiments.

Furthermore, our algorithm to select suitable FWL word widths to model
plant behaviour employs a heuristic based on user-provided controller
word-width specifications.  Given the encouraging results of our benchmarks,
this heuristic appears to be strong enough for the current benchmark set,
but this may not generalise.  Further experiments towards determining
suitable plant FWL configurations may thus be necessary in future work.
